Twists of supersymmetric gauge theories

### 2019-11-11 paper.tex
merge

\subsection{Dimension 7}
The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.  It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.

In 7 dimensions, exactly like in 8-dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Rank 1 pure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)=0$.  Such supercharges are minimal: they have 4-dimensional image in $\CC^7$.
 \item Rank 1 impure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)\ne 0$.  Such supercharges are topological.
 \item Rank 2 square-zero spinors, i.e. square-zero elements of the form $Q = \alpha_1 \otimes w_1 + \alpha_2 \otimes w_2$, where $w_1$ and $w_2$ are linearly independent.  Such supercharges have a 5-dimensional image in $\CC^7$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded. 
\end{enumerate}

The three twists of 7-dimensional $\mc N=1$ super Yang-Mills theory can be calculated by dimensionally reducing the twists of 8-dimensional super Yang-Mills.

\begin{theorem} \label{7d_holo_twist_thm}
The minimal twist of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ and an oriented 1-manifold $L$ is equivalent to mixed BF theory on the product $X_3 \times L_{\mr{dR}}$. This twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times L_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
\end{theorem}

\begin{proof}

\end{proof}

\begin{theorem} \label{7d_rank2_twist_thm}
The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau surface $X_2$ with an oriented 3-manifold $M_3$ is equivalent to mixed Chern-Simons theory on $X_2 \times (M_3)_{\mr{dR}}$. \chris{actually I need to think about the twisting homomorphism here.}
\end{theorem}

\begin{proof}

\end{proof}

@@

There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
\begin{align*}
S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi \\
&\brian{where does this term come from \pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R}
\end{align*}
\brian{add terms involving antifields}

@@

The action of supersymmetry on the gauge sector is encoded by the functionals:
\begin{align*}
I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda_+ + \lambda_-)\> + \<\lambda_+^*+\lambda_-^*, \sd F_A (Q_+ + Q_-)\> \\
I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda_+^*+\lambda_-^*) Q_- + (Q_-, \lambda^*_+ + \lambda_-^*)Q_+)\right\> .
\end{align*}

@@

The computation of the remaining terms in the matter sector are summarized in the following lemma. 
\begin{lem}
\[
\d_{CE} I_{\rm Poin} + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\} = 0.
\]
\end{lem}
\begin{proof}

>>>>

\subsection{Dimension 7}

% \cN=1 SYM, three twists identical to dimension 8

@@

There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
\begin{align*}
S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi
\end{align*}
\brian{add terms involving antifields}
\brian{There is a term of the form $\pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R$ that is usually written down.
This indeed changes the EOM, and is needed to compensate an extra term in the definition of $I_{\rm gauge}^{(1)}$ when we couple to matter. My claim is that if we disregard both of these terms we will get a consistent supersymmetric system still.
}

@@

The action of supersymmetry on the gauge sector is encoded by the functionals:
\begin{align*}
I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda_+ + \lambda_-)\> + \<\lambda_+^*+\lambda_-^*, \sd F_A (Q_+ + Q_-)\> \\
I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda_+^*+\lambda_-^*) Q_- + (Q_-, \lambda^*_+ + \lambda_-^*)Q_+)\right\> .
\end{align*}
\brian{C and P claim there should be some extra terms in $I^{(2)}_{\rm gauge}$ coming from reduction. 
If a few of those terms are of the form $\<\lambda_-^*, \lambda_-^*\>\<Q_-,Q_-\>$ and $\<\lambda_+^*, \lambda_+^*\>\<Q_+,Q_+\>$ we'd be in business. 
The issue is that in the twist calculation below has an extra copy of a complex involving components of $\lambda_-^*$ in degree zero and $\lambda_-$ in degree $+1$.
Such terms would turn this acyclic.
Can we see why such terms are {\em necessary} to preserve off-shell SUSY?
}

@@

The computation of the remaining terms in the matter sector are summarized in the following lemma. 
\begin{lem}
\[
\d_{CE} I_{\rm Poin} + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\} = 0.
\]
\end{lem}
\brian{extra terms in $I^{(2)}$?}
\begin{proof}
